Effect of Election on Currency Fluctuation

### 2024-04-10 paper/paper.qmd
tested model in the appendix

ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = "none") +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

@@

# Model

@@

\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}

@@

# Results

@@

```{r}
colors <- c("No Inauguration Announcement" = "yellow", "Inauguration Announcement" = "blue")

@@

# Discussion

## First discussion point {#sec-first-point}

@@

## Second discussion point

@@

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...

@@

pp_check(first_model) +
  theme_classic() +
  theme(legend.position = "bottom")

posterior_vs_prior(first_model) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```

@@

@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...

@@

plot(first_model, "trace")

plot(first_model, "rhat")
```

>>>>

@@

# Model {#sec-model}

@@

$$y_i|\mu_i, \sigma \sim \mbox{Normal}(\mu_i, \sigma)$$

$$\mu_i = \alpha + \beta_i + \omega_i$$

$$\alpha \sim \mbox{Normal}(0, 2.5)$$

$$\beta \sim \mbox{Normal}(0, 2.5)$$

$$\omega \sim \mbox{Normal}(0, 2.5)$$

$$\sigma \sim \mbox{Exponential}(1)$$

Where:

-   $y_i$ is the daily exchange rate of USD v.s. CAD (base unit is CAD = 1)

-   $\beta_i$ is a dummy variable (value is either 0 or 1) indicating whether the date is within the inauguration week (see data section for definition of inauguration week). If date is within the inauguration week, then the variable has a value of 1, and 0 otherwise.

-   $\omega_i$ is a dummy variable indicating whether a change of political party occurred in the corresponding election season. Each inauguration week receives identical value (the whole week is either all 1 or all 0). Value of 1 indicates that the elected president's political party is different from last season's president's, 0 otherwise.

@@

# Results {#sec-results}

@@

## Explaination for small R^2
```{r}
colors <- c("No Inauguration Announcement" = "yellow", "Inauguration Announcement" = "blue")

@@

# Discussion {#sec-discussion}

## Expectation of the population

@@

## Change of Political Party

@@

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. We can see that the regression outcome from our data and the simulation created by the posterior distribution are not closely matched. This is because our predictor variables only contribute to a small section of the data (40 out of 13358 observations has inauguration_period == 1, 30 out of 13358 has change_party == 1).

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. We can see that the estimation parameters shifts minimally after taking data into account. This suggests that good prior parameters were set.

@@

pp_check(inaug_model) +
  theme_classic() +
  theme(legend.position = "bottom")

posterior_vs_prior(inaug_model) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```

@@

@fig-stanareyouokay-1 is a trace plot. Trace plots are often used to diagnose abnormalities of models. For both plots, lines are oscillating vertically and maintains an overall horizontal trend. This suggests that there is nothing out of the ordinary for our model.

@fig-stanareyouokay-2 is a Rhat plot. Rhat plot is a valuable tool for assessing convergence in Bayesian regression models, helping ensure the reliability and validity of the model's inference results. Both both plots, all data points are close to 1. This suggest that there is nothing out of the ordinary for our model.

@@

plot(inaug_model, "trace")

plot(inaug_model, "rhat")
```
